Brief Article

### 2012-05-08 visual-classical.tex
updated glossary

\begin{tabular}{lp{4in}}
$H_0$ & the data plot is consistent with the null distribution \\
$H_a$ & \\
test statistic & data plot inserted into a lineup of $m-1$ null plots, that are created consistently with the null hypothesis.\\
sampling distribution & \\
Significance level $\alpha$ & $\alpha \in (0,1)$ is the threshold at which we will reject the null hypothesis, should the $p$-value fall under it, usually $\alpha=0.05$.\\
test procedure & a set of $K$ independent judges evaluates a lineup of size $m$ to come to a conclusion whether to reject $H_0$.\\
$p$-value & probability that $x$ or more of $K$ observers pick the data plot  under $H_0$. \\
Power & probability to reject the null hypothesis\\
Type I error & probability to reject the null hypothesis if it is true\\
Type II error & probability to fail to reject the null hypothesis if it is false\\
\end{tabular}

>>>>

\begin{tabular}{lp{4in}}
$H_o$ & Null hypothesis, of the essence that there is nothing interesting to see in this data. \\
$H_a$ & Alternative hypothesis, of the essence that the patterns seen in the data are inconsistent with randomness, without a need to be very specific. \\
Test statistic & Plot of the data data, designed to be able to detect interesting as defined by the null and alternative hypotheses\\
Null plot & Plot of data that is generated in a manner consistent with the null hypothesis. Sometimes the distribution that this data is drawn from is considered to be the null distribution. \\
Sampling distribution & Distribution of the test statistic, assuming that the null hypothesis is true. When a lineup is used to test the null hypothesis a small, finite number of samples is drawn from the null distribution, and plotted in the same manner as the test statistic. This forms the sampling distribution upon which the test is made.  \\
Significance level, $\alpha$ & $\alpha \in (0,1)$, usually $\alpha=0.05$, is the threshold value at which we will reject the null hypothesis. Because a small finite number of null plots are shown along with the data, the significance level will be 1/(\# of plots in the lineup) for one observer. For multiple observers, $\alpha$ might be set to be lower than 0.05. \\
%test procedure & a set of $K$ independent judges evaluates a lineup of size $m$ to come to a conclusion whether to reject $H_0$.\\
$p$-value & By definition, the $p$-value is the probability the data plot is recognizable as different from the null plots, assuming that the null hypothesis is true. For multiple observers, this can be estimated by assuming that the chance that the data plot is chosen by one observer is $p=0.05$ (typically), and accounting for the mulitple picks using a Beta distribution. \\
Power & Defined as the probability of rejecting the null hypothesis, when the null hypothesis is not true. This is estimated from the trials as the proportion, number of observers who pick the data plot/total number of observers. \\
Type I error & The probability of rejecting the null hypothesis if it is actually true. This is typically controlled at the value $\alpha$. \\
Type II error & The probability of failing to reject the null hypothesis if it is not true.\\
\end{tabular}
